I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-07-20 paper_io_sim.tex
Revision

	\section{Introduction}
		\begin{itemize}
			\item HPC, the bottleneck in I/O and the demand of HPC experiments. 
			\item Difficulties in conducting high performance computing experiments and the need of simulation frameworks.
			\item Existing experiment methods, simulators, simulation frameworks. The advantages of SimGrid compared to others \cite{casanova2008, lebre2015}. The missing of the ability to simulate page cache in SimGrid \cite{lebre2015}.
			\item The objective of the paper: Add capability to simulate I/O with page cache in SimGrid.
		\end{itemize}
	\section{Related Work}

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works \cite{linuxdev3rd2010}. Effects and importance of page cache.
				\item Introduce some existing strategies with some highlighted pros and cons.
				\item Current implementation in Linux and some reasons why it is chosen to be implemented (implementation complexity, effectiveness, overhead, etc) \cite{linuxdev3rd2010}
				\item \tristan{LRU lists are mentioned in the next section, they should be described here.}
			\end{itemize}

		\subsection{Simulators}
			\begin{itemize}
				\item Discuss some existing methods, simulation frameworks to conduct HPC experiments. Compare pros and cons (accuracy, simulation time, usability) of some simulators (SimGrid, GridSim).
				\item Related development: RAM energy consumption \cite{gill2019} \cite{ouarnoughi2017} 
				\item Discuss the pros of SimGrid and the reasons why we chose it to extend. (Section 2.2.2 in \cite{casanova2014})
				\item \tristan{Mention the status of storage simulation in simulators, so that we understand from Fig 1 that storage devices are available}
			\end{itemize}

	\section{Method}
		In this section, we present our approach to model file read/write,
		memory I/O, cache eviction and data flushing mechanisms implemented in
		the Linux kernel. We also detail the design of our simulators and their
		implementation. Finally, we describe experimental scenarios to evaluate
		our simulation model on real applications using a standalone Python
		prototype, the current SimGrid simulator, and our extension of SimGrid.

@@

            We separate our simulation model in two components, the IO
			Controller and the Memory Manager, which together simulate Linux
			kernel I/Os (Figure~\ref{fig:interaction}). The Memory Manager
			simulates memory I/O, flushing, and cache eviction, whereas the IO
			Controller simulates file reads and writes. Simulated applications
			can simply interact with the IO Manager instead of calling simulated
			storage directly as is the case with current simulators.

@@

			We leverage existing storage simulation models to simulate the memory,
			which is characterized with capacity, read and write bandwidths. 
			This can be done when disks are modeled with distinguished read/write 
			bandwidths and negligible disk latency, which is applicable to memory 
			\cite{lebre2015}. In addition, leveraging existing disk models allows us 
			to take advantage of bandwidth sharing between concurrent disk I/O to 
			simulate parallel memory accesses.\tristan{we should refer to related work, 
			see comment there}.

			We introduce the concept of a data block as a unit to represent data
			cached in memory. A data block is a subset of file pages stored in
			page cache that were accessed in the same read or write operation. 
			A data block has information about file name, block size, last access 
			time, and a dirty flag that represents whether the data is clean (0) 
			or dirty (1). 
			A given file can have multiple data blocks in page cache. In
			addition, a data block can be split into an arbitrary number of
			smaller blocks, and data blocks can be merged together.

			We simulate the kernel LRU lists of file pages
			with two lists of data blocks: an active list and 
			an inactive list, ordered by last access time (earliest first, see 
			Figure~\ref{fig:lrulist}).
			As in the kernel, our simulator keeps the size of the active list under
			twice the size of the inactive list by moving least recently 
			used data blocks from the active list to the inactive list. 
			Modeling page cache LRU lists as lists of data blocks reduces the
			overhead of the simulator, as data blocks are obviously less
			numerous than file pages, while preserving the accuracy in I/O time
			simulation \tristan{how do you know that, can you provide an argument?}.

			\begin{figure}
   				\centering
   				\includegraphics[width=\columnwidth]{figures/lru_lists.pdf}
   				\caption{Simulation of page cache LRU lists with data blocks}\label{fig:lrulist}
			\end{figure}

			The simulated LRU lists are used as follows. When a file is read, 
			file data can be partially cached, completely cached, or uncached. 
			For cached data, there are existing data blocks representing 
			this data in two page cache LRU lists. 
			As this cached data is accessed again, these blocks are moved to 
			the active list, dirty blocks are merged into a bigger dirty block, 
			while clean data blocks are merged into another clean block. 
			If data read is not in cache, a clean block representing uncached data 
			is created and put into the top of the inactive list.

@@

			We also keep the size of the active list not larger than twice the size of 
			the inactive list as in the kernel 
			\cite{gorman2004understanding, linuxdev3rd2010}. 
			This is done by moving least recently used blocks in the active list 
			to the inactive list when the active list grows. If only a part of a data 
			block needs to be moved, the block is split.

@@

			\begin{algorithm}\caption{File read simulation}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size (assumed to fit in memory)}
						\Desc{mm}{MemoryManager object}
						\Desc{sm}{storage simulation model}
   					\EndInput
					\State mm.flush(2*fs - mm.cached(fn) - mm.evictable\_mem) 
					\State mm.evict(2*fs - mm.cached(fn) - mm.free\_mem) 
					\If {mm.cached(fn) $>$ 0}  \Comment{Read file cached data}
					    \State mm.periodic\_flush() \Comment{Flush during cache read}
    					\State mm.cache\_read(fn) 
					\EndIf
					\If {mm.cached(fn) $<$ fs} \Comment{Read uncached data from disk}
						\State mm.periodic\_flush() \Comment{Sequential with disk read}
						\State mm.add\_to\_cache(fs - mm.cached(fn), fn)
    					\State sm.read(fs - mm.cached(fn))
					\EndIf

@@

			The algorithm to simulate file reads is described in 
			Algorithm~\ref{alg:read}.   
			In Linux systems, data can be either read from cache with memory bandwidth 
			or read from disk with disk bandwidth. 
			Therefore, total read time can be considered as sequential reads with 
			these different bandwidths, enabling us to generalize reading process as 
			two separate phases, cache read and disk read. 
			When a simulated application reads a file, it sends a file read request 
			to IO Controller. 
			First, if there is not enough memory available to store two
			copies of the file (one in cache, one in anonymous memory), the
			Memory Manager is called to flush dirty data to disk and simulate 
			flushing time with memory model (line 6).
			This flushing is complemented by eviction by the Memory Manager (line 7). 
			Next, if the file is cached, either partially or entirely, data is read from 
			cache first. Periodical flushing is triggered at the beginning of the 
			cache read to flush dirty data if some dirty data is expired (line 9).
			At the same time, Memory Manager is called to read data from cache, 
			and update the corresponding data blocks in cache (line 10). 
			The concurrency of periodical flushing and cache read is handled and 
			time is simulated by the memory and disk models.

			If file is not cached or partially cached, a disk read is required (line 12). 
			Periodical flushing is called again at the beginning of the disk read 
			(line 13), the storage model simulates the disk write with the remaining 
			amount of data (line 14), and data read from disk is added to cache 
			(line 15). Similar to cache read period, disk bandwidth sharing is handled 
			and time is simulated by storage models.

@@

			Algorithm~\ref{alg:write} describes our simulation of file write. 
			Initially, periodical flushing is called to asynchronously flush expired 
			dirty data at the beginning of the write (line 6).
			Similar to the file read simulation, a file can also be written with 
			two different bandwidths, memory bandwidth and disk bandwidth. 
			Data can be written with memory bandwidth before the amount 
			of dirty data reaches dirty\_ratio. Thus, our algorithm initially checks 
			the amount of data that can be written with memory write 
			bandwidth (line 7-8).
			If this amount is greater than 0, MemoryManager is asked to evict 
			data from cache to accommodate the written data if needed (line 10). 
			Then, cache write is simulated with memory model and data written is 
			added to page cache LRU lists (11).
			The amount of data that is not written with memory bandwidth is written 
			with disk bandwidth (line 13). 
			Now, the dirty ratio threshold is reached, we have to flush and evict 
			data from cache as much as possible so that 
			the remaining data can be written to cache (line 14-15). 
			Here, MemoryManager does not guarantee that the amount of flushed 
			and evicted data is enough for the remaining data. In the case it is 
			less than the required amount, the remaining data is written to cache 
			but then can be flushed and evicted right away. Thus, the amount 
			of remaining data that is written and kept in cache after the write 
			is limited by the amount free memory (line 16). 
			Finally, the disk write is simulated with the remaining amount of 
			data (line 17). As in the simulation of file read, all the concurrent 
			cache write and disk write are simulated by memory and disk models.

@@

			Since bandwidth sharing is not simulated, this prototype doesn't support 
			concurrency: it is limited to single-threaded pipelines running on systems 
			with a single-core CPU. We use it in a first validation of our simulation 
			model, against a real sequential pipeline running on a real system.
			Source code of our Python prototype is available at 
			https://github.com/big-data-lab-team/paper-io-simulation/tree/master/exp/pysim

			Having our model validated, we create simulators for different use cases 
			using the current version of SimGrid and the SimGrid version that is 
			extended with our model. To simulate our pipelines and system, we leverage 
			the Workflow Management System Simulation Workbench 
			(WRENCH~\cite{wrench}), a framework  built over SimGrid.
		    We compare the results of the simulators with
			original SimGrid and extended SimGrid with the results of real
			pipelines on a real system.

			\textcolor{red}{[Description, implementation of our SimGrid extension]}.

@@

			The goal of our experiments is to evaluate our write-back cache
			simulation in single-threaded and multi-threaded applications
			accessing data on different types of file system. We use a pipeline
			of sequential tasks where each task reads an input file, increments
			every byte of the input to emulate real processing and avoid caching
			effects, and writes the result to disk. The output of the previous
			task is the input of the next task. We also use a real application 
			pipeline, to evaluate the applicability of oursimulation model.

			We use our dedicated cluster hosted at Concordia University to conduct 
			the experiments. The cluster consists of one login node, 8 compute nodes 
			and 4 storage nodes connected with two network switches. The login node 
			has one Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 128GiB of RAM, 1.8TB 
			of storage of XFS file system, 13GB of tmpfs file system and 385 TB of 
			Lustre shared file system. Each compute node has two 16 cores Intel(R) 
			Xeon(R) Gold 6130 CPU @ 2.10GHz, 256 GB of RAM and 6 SSDs, 450GB each 
			with XFS file system, 378GB of tmpfs and 126GB of devtmpfs file system.
			Lustre file system is configured with one metadata target with 854GB 
			of storage, 44 object storage targets with 8.7TB of storage each. 
			The cluster is run on CentOS 8.1 with the Slurm Workload Manager installed. 
			We use \textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to 
			monitor and collect data of memory, page cache status and disk throughput 
			on the cluster. 
			\textcolor{red}{[Add network description here, include number of disks 
			on all nodes ,maybe add a diagram]}

@@

			The pipeline used in this experiment consists of three tasks, 
			each task reads a file, increases every byte and writes output file 
			to local disk. 
			We use the input sizes of 20 GB, 50 GB, 75 GB and 100 GB, run 
			the pipeline on the cluster, measure the CPU time of the tasks  
			with each input and use it to simulate CPU time in the simulators .

@@

			We simulate this pipeline with a simulator with original SimGrid and 
			extended SimGrid. 
			The simulation results are then compared with the real results. 
			Because our work focuses on I/O time, we assume that CPU time is 
			correctly modeled and use the CPU time measured in the real pipelines 
			to setup our simulated workflow. The results are compared in terms of 
			I/O time and total makespan.

@@

			\item Quantitative results: 
				\begin{itemize}
					\item Errors of simulation time and memory used compared to real results.
					\item Simulation time compared to baseline SimGrid.
				\end{itemize}

@@

	\section{Discussion and Future Work}
		\begin{itemize}
			\item Sensitivity of the simulator on the variation of memory and disk bandwidth. 
		\end{itemize}
	\section{CFI for cluster}
\bibliographystyle{plain}
\bibliography{citation}

>>>>

	\section{Introduction}
		\begin{itemize}
			\item HPC, the bottleneck in I/O and the demand of HPC experiments. 
			\item Difficulties in conducting high performance computing experiments and the need of simulation frameworks.
			\item Existing experiment methods, simulators, simulation frameworks. The advantages of SimGrid compared to others \cite{casanova2008, lebre2015}. The missing of the ability to simulate page cache in SimGrid \cite{lebre2015}.
			\item The objective of the paper: Add capability to simulate I/O with page cache in SimGrid.
			\item Clarify, distinguish between memory I/O (i/o to page cache) and disk I/O.
		\end{itemize}
	\section{Related Work}

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works \cite{linuxdev3rd2010}. 
				Write-back vs writethrough and direct i/o. Effects and importance of page cache.
				\item Introduce some existing strategies with some highlighted pros and cons.
				\item Current implementation in Linux and some reasons why it is chosen to be implemented (implementation complexity, effectiveness, overhead, etc) \cite{linuxdev3rd2010}
				\item \tristan{LRU lists are mentioned in the next section, they should be described here.}
			\end{itemize}

		\subsection{Simulators}
			\begin{itemize}
				\item Discuss some existing methods, simulation frameworks to conduct HPC experiments. Compare pros and cons (accuracy, simulation time, usability) of some simulators (SimGrid, GridSim).
				\item Related development: RAM energy consumption \cite{gill2019} \cite{ouarnoughi2017} 
				\item What is implemented in simulators that useful for our model:
				distinguished and shared bandwidths, concurrency, device latency. 
				\item Discuss the pros of SimGrid and the reasons why we chose it to extend. (Section 2.2.2 in \cite{casanova2014})
				\item \tristan{Mention the status of storage simulation in simulators, so that we understand from Fig 1 that storage devices are available}
			\end{itemize}

	\section{Method}

		In this section, we present our approach to model file read and write with
		I/O to page cache, cache eviction and data flushing mechanisms implemented 
		in the Linux kernel. We also detail the design of our simulators and their
		implementation. Finally, we describe experimental scenarios to evaluate
		our simulation model on real applications using a standalone Python
		prototype, the current SimGrid simulator, and the SimGrid version that is 
		extended with our simulation model (SimGridExt).

@@

            We separate our simulation model in two components, the IO
			Controller and the Memory Manager, which together simulate 
			file read/write mechanisms in Linux (Figure~\ref{fig:interaction}). 
			The Memory Manager simulates I/Os to cache, flushing, and cache eviction, 
			whereas the IO Controller simulates file reads and writes. 
			Simulated applications can simply interact with the IO Manager instead of 
			calling simulated storage directly as is the case with current simulators.

@@

			We leverage existing storage simulation models to simulate the memory,
			which is characterized by storage capacity, distinguished read/write 
			bandwidths and device latency. 
			All of these features are dealt within models in simulation 
			frameworks, which makes storage models applicable to memory \cite{lebre2015}. 
			In addition, leveraging existing disk models allows us 
			to take advantage of bandwidth sharing between concurrent disk I/O to 
			simulate parallel memory accesses.\tristan{we should refer to related work, 
            see comment there} \valerie{Agreed. It's unclear how existing storage models enable this at the moment}.

			In Linux kernel, the page cache LRU lists contain file pages. However, 
			due to the large number of file pages, managing lists of pages may 
			require significant computation overhead. 
			Thus, we introduce the concept of a data block as a unit to represent data 
			cached in memory. A data block is a subset of file pages stored in
            page cache that were accessed in the same read or write operation. 
			A data block has information about file name, block size, last access 
			time, and a dirty flag that represents whether the data is clean (0) 
			or dirty (1). 
			A given file can have multiple data blocks in page cache. In
			addition, a data block can be split into an arbitrary number of
			smaller blocks, and data blocks can be merged together.

			\begin{figure}
   				\centering
   				\includegraphics[width=\columnwidth]{figures/lru_lists.pdf}
   				\caption{Simulation of page cache LRU lists with data blocks}	\label{fig:lrulist}
			\end{figure}

			Now, page cache LRU lists can be modeled with two lists of data blocks: 
			an active list and an inactive list, ordered by last access time 
			(earliest first, see Figure~\ref{fig:lrulist}).
			As in the kernel, our simulator keeps the size of the active list under
			twice the size of the inactive list by moving least recently 
            used data blocks from the active list to the inactive list.
			Modeling page cache LRU lists as lists of data blocks reduces the
			overhead of the simulator, as data blocks are obviously less
			numerous than file pages, while preserving the accuracy in I/O time
			simulation \tristan{how do you know that, can you provide an argument?}.

			Given an arbitrary file, at a specific time, its data can be partially 
			cached, completely cached, or uncached.
			Cached data can be composed of data blocks existing in either or both
            of the page cache LRU lists. Cached blocks reside in the inactive list
            unless they have been recently been reaccessed. Cached blocks 
            located on the inactive list that are subsequently accessed, 
            will be moved to the top of the active list. Cached blocks 
            recently written to cache are dirty until they are flushed to disk.

            The simulated LRU lists are used as follows. When a file is read, 
            as mentioned, its data can be partially cached, completely cached, 
            or uncached. 
            For cached data, there are existing data blocks representing
			this data in two page cache LRU lists. 
			As this cached data is accessed again, these blocks are moved to 
			the active list, dirty blocks are merged into a bigger dirty block, 
			while clean data blocks are merged into another clean block. 
			If data read is not in cache, a clean block representing uncached data 
			is created and put into the top of the inactive list.

@@

			\textcolor{red}{[Is there any kind of accesses other than read and write? 
			Should we mention them?]}.

            As done in the kernel, we ensure the size of the active list does not exceed twice the size of 
			the inactive list 
			\cite{gorman2004understanding, linuxdev3rd2010}. 
			This is done by moving least recently used blocks in the active list 
			to the inactive list when the active list grows. If only a part of a data 
			block needs to be moved, the block is split.

@@

			\begin{algorithm}\caption{File read simulation}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size (assumed to fit in memory)}
						\Desc{mm}{MemoryManager object}
						\Desc{sm}{storage simulation model}
   					\EndInput
					\State mm.flush(2*fs - mm.cached(fn) - mm.evictable\_mem) 
					\State mm.evict(2*fs - mm.cached(fn) - mm.free\_mem) 
					\State mm.periodic\_flush() \Comment{Periodically flush expired dirty data}
					\If {mm.cached(fn) $>$ 0}  \Comment{Read file cached data}
    					\State mm.cache\_read(fn)  \Comment{Update cached data}
					\EndIf
					\If {mm.cached(fn) $<$ fs} \Comment{Read uncached data from disk}
						\State sm.read(fs - mm.cached(fn)) \Comment{Simulated disk read}
						\State mm.add\_to\_cache(fs - mm.cached(fn), fn)
					\EndIf

@@

			The algorithm to simulate file reads is described in Algorithm~\ref{alg:read}.   
%			In Linux systems with page cache, data can be either read from cache 
%			or read from disk with disk bandwidth. 
%			Therefore read time can be considered as the sum of the time required to 
%			read from all devices\valerie{Can you clarify if disk+memory writes are not concurrent }, enabling us to generalize reading process as 
%			two separate phases, cache read and disk read. 
			In Linux systems with page cache, data can be either read from cache 
			or read from disk concurrently. As this concurrency is modeled in simulation 
			frameworks, we simulate a file read as follows.
			When a simulated application reads a file, it sends a file read request 
			to IO Controller. 
			First, if there is not enough memory available to store two
			copies of the file (one in cache, one in anonymous memory), the
			Memory Manager is called to flush dirty data to disk and simulate 
			flushing time with memory model (line 6).
			This flushing is complemented by eviction by the Memory Manager (line 7). 
			In lines 6-7, we assume that user applications require the amount of memory 
			equal to the file size, making total required memory twice the size of 
			the file. Apart from flushing a required amount of memory, periodical 
			flushing is then triggered to flush expired dirty data (line 8).
			Next, if the file is cached, either partially or entirely, data is read from 
			cache first (line 9). Memory Manager is called to read data from cache, 
			update the corresponding data blocks in cache (line 10).

			If file is not cached or partially cached, a disk read is required (line 12). 
			The storage model simulates the disk read with the remaining 
            amount of data (line 13), and data read from disk is added to 
            cache (line 14). The total file read time is simulated at the end of the algorithm. 
            During the entire file read, the concurrency between periodical flushing, 
            cache read and disk read is handled by storage models.

@@

            \valerie{I think we need to take periodic flush out as it shouldn't be added to the write time}

			Algorithm~\ref{alg:write} describes our simulation of file write. 
			Initially, periodical flushing is called to asynchronously flush expired 
			dirty data at the beginning of the write (line 6).
			During file write simulation, a file is cached in memory and also written 
			to disk. Data can be written to cache without waiting for flushing or 
			being throttled before the amount of dirty data reaches dirty\_ratio. 
			Thus, our algorithm initially checks the amount of data that can be written 
			with memory write bandwidth (line 7-8).
			If this amount is greater than 0, MemoryManager is asked to evict 
			data from cache to accommodate the written data if needed (line 10). 
			Then, cache write is simulated with memory model and data written is 
			added to page cache LRU lists (11).
			After dirty\_ratio is reached, dirty data has to be flushed before new data 
			is written to cache again. 
			We flush and evict data from cache as much as possible so that the 
			remaining data can be written to cache (line 14-15). 
			Here, MemoryManager does not guarantee that the amount of flushed 
			and evicted data is enough for the remaining data. In the case it is 
			less than the required amount and existing dirty data can not be flushed, 
			the remaining data being written to cache can be flushed and evicted right away. 
			Thus, the amount of remaining data written and kept in cache 
			after the write is limited by the amount free memory, and this amount 
			is added to cache (line 16). 
			Finally, the disk write is simulated with the remaining amount of 
			data (line 17). As in the simulation of file read, all the concurrency  
			of cache write and disk write are simulated by memory and disk models.

@@

			Since bandwidth sharing is not simulated, this prototype doesn't support 
			concurrency: it is limited to single-threaded pipelines running on systems 
			with a single-core CPU. We use it in a first validation of our simulation 
			model, against a real sequential pipeline running on a real system.
			Source code of our Python prototype is available at 
            \url{https://github.com/big-data-lab-team/paper-io-simulation/tree/master/exp/pysim}

			Having our model validated, we create simulators for different use cases 
			using original SimGrid and our SimGridExt version. 
			To simulate our pipelines and system, we leverage 
			the Workflow Management System Simulation Workbench 
			(WRENCH~\cite{wrench}), a framework  built over SimGrid.
		    We compare the results of the simulators with
			original SimGrid and extended SimGrid with the results of real
			pipelines on a real system.

			\textcolor{red}{[Description, implementation of our SimGridExt]}.

@@

        	The goal of our experiments is to evaluate our write-back cache 
			simulation in single-threaded and multi-threaded applications
			accessing data on different types of file system. We use a pipeline
			of sequential tasks where each task reads an input file, increments
			every byte of the input to emulate real processing and avoid caching
			effects, and writes the result to disk. The output of the previous
			task is the input of the next task. We also use a real application 
            pipeline \textcolor{red}{[Maybe briefly describe this application's purpose (e.g. a standard fMRI preprocessing piepeline)]}, to evaluate the applicability of our simulation model.

			We use our dedicated cluster hosted at Concordia University to conduct 
			the experiments. The cluster consists of one login node, 8 compute nodes 
			and 4 storage nodes connected with two network switches. The login node 
			has one Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 137~GB (128~GiB) of RAM, 
			1.8TB of storage of XFS file system, 13~GB of tmpfs file system and 385 TB of 
			Lustre shared file system. Each compute node has two 16 cores Intel(R) 
			Xeon(R) Gold 6130 CPU @ 2.10GHz, 275~GB (256~GiB) of RAM and 6 SSDs, 
			450~GB each with XFS file system, 378~GB of tmpfs and 126~GB of devtmpfs file system.
			Lustre file system is configured with one metadata target with 854~GB 
			of storage, 44 object storage targets with 8.7~TB of storage each. 
			The cluster is run on CentOS 8.1 with the Slurm Workload Manager installed. 
			We use \textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to 
			monitor and collect data of memory, page cache status and disk throughput 
			on the cluster. 
			\textcolor{red}{[Add network description here, include number of disks 
			on all nodes ,maybe add a diagram]}

@@

			The pipeline used in this experiment consists of three tasks, 
			each task reads a file, increases every byte and writes output file 
			to local disk. 
			We use the input sizes of 20~GB, 50~GB, 75~GB and 100~GB, run 
			the pipeline on the cluster, measure the CPU time of the tasks  
			with each input and use it to simulate CPU time in the simulators .

@@

			We simulate this pipeline with a simulator with original SimGrid and 
			extended SimGrid. 
			The simulation results are then compared with the real results. 
			Because our work focuses on I/O time, we assume that CPU time is 
			correctly modeled and use the CPU time measured in the real pipelines 
			to setup our simulated workflow. The results are compared in terms of 
			read/write time and total makespan.

@@

			\item Quantitative results: 
				\begin{itemize}
					\item Relative errors of simulation time and memory used compared to real results.
					\item Simulation time compared to baseline SimGrid.
				\end{itemize}

@@

	\section{Discussion and Future Work}
		\begin{itemize}
			\item Sensitivity of the simulator on the variation of memory and disk bandwidth. 
			\item Our model does not support random I/O and readahead.
		\end{itemize}
	\section{CFI for cluster}
\bibliographystyle{plain}
\bibliography{citation}
